\textbf{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}\\Online Appendix

### 2018-09-27 redaction/online_appendix_travail.tex
Petits changements divers

One explanation of these contrasted results lies in the share of primary goods in total flows. It is reported in Figure \ref{fig:Share_prim_goods}. In air transport, the share of primary goods in the total value of US imports is very small, around 10\% all over the period from 1974 to 2014. Primary goods make a higher proportion of trade flows in vessel transport, especially over 1974-1982 (between 40\% and 60\%). On the following sub-period though, their share has fallen to 20-30\%. Given the modest proportion of primary goods in total imports flows of the US economy compared to the manufactured sector, it is hence not surprising that the diagnosis made about the time trend of transport costs when all types of flows are considered is driven by the trend patterns that occur within the manufacturing sector. \\
Still, it is interesting to notice that composition effects are not dominated by changes in the primary goods share. If they were, we would not observe the same trends for trade as the whole and trade of manufactured goods.

>>>>

One explanation for the similarity between the results for the manufacturing goods trade and for total trade can be found in the share of primary goods in total flows as reported in Figure \ref{fig:Share_prim_goods}. In air transport, the share of primary goods in the total value of US imports is very small, around 10\%. Primary goods make a higher proportion of trade flows in vessel transport, especially over 1974-1982 (between 40\% and 60\%). On the following sub-period though, their share has fallen to 20-30\%. Given the modest proportion of primary goods in total import flows of the US economy compared to the manufactured sector, it is hence not surprising that the diagnosis made about the time trend of transport costs when all types of flows are considered is driven by the trend patterns that occur within the manufacturing sector.
